Combining network-guided GWAS to discover susceptibility mechanisms for breast cancer

### 2020-08-20 manuscript/manuscript.tex
compiled final version
updated manuscript's affiliations and contributions

\documentclass[draft,twocolumn, 11pt]{article}
\usepackage{amsmath,amssymb}
\usepackage[format=hang,labelfont=bf,textfont=small,singlelinecheck=false,justification=justified,margin={20pt,20pt},figurename=Fig.]{caption}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{grffile}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\usepackage{threeparttable}
\usepackage[numbers]{natbib}
\usepackage{lmodern} % Chloe: better font rendering
\usepackage[shortcuts]{extdash} 
\newcommand{\mean}[1]{$\overline{\mbox{#1}}$}
\newcommand{\median}[1]{$\hat{\mbox{#1}}$}

@@

\title{Combining network-guided GWAS to discover susceptibility mechanisms for breast cancer}
\author{Héctor Climente-González$^{1,2,3}$, Christine Lonjou$^{1,2,3}$, Fabienne Lesueur$^{1,2,3}$, \\
GENESIS Study collaborators$^{1,2,3}$, Dominique Stoppa-Lyonnet$^{4,5,6}$, \\
Nadine Andrieu$^{1,2,3}$, Chloé-Agathe Azencott$^{3,1,2}$}
\date{$^{1}$Institut Curie, PSL Research University, F-75005 Paris, France;\\
  $^{2}$INSERM, U900, F-75005 Paris, France;\\
  $^{3}$MINES ParisTech, PSL Research University, CBIO-Centre for Computational Biology, F-75006 Paris, France;\\
  $^{4}$Service de Génétique, Institut Curie, F-75005 Paris, France;\\
  $^{5}$INSERM, U830, F-75005 Paris, France;\\
  $^{6}$Université Paris Descartes.\\
}
\hypersetup{
  pdfauthor={Héctor Climente-González, Christine Lonjou, Fabienne Lesueur, GENESIS Study collaborators, Dominique Stoppa-Lyonnet, Nadine Andrieu, Chloé-Agathe Azencott},
  pdftitle={Combining network-guided GWAS to discover susceptibility mechanisms for breast cancer},
  pdfkeywords={},
  pdfsubject={},
  pdflang={English}}
\begin{document}

@@

H.C-G. conducted all the final analyses and the wrote the manuscript. C.L. conducted analyses using LEAN, Sigmod, and dmGWAS, and provided technical and scientific help and feedback. F.L. and N.A. provided feedback on the analyses and the manuscript. C-A.A. supervised the project. N.A and D.S-L lead the GENESIS study.

>>>>

\documentclass[twocolumn, 11pt]{article}
\usepackage{amsmath,amssymb}
\usepackage[format=hang,labelfont=bf,textfont=small,singlelinecheck=false,justification=justified,margin={20pt,20pt},figurename=Fig.]{caption}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{grffile}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\usepackage{threeparttable}
\usepackage[numbers]{natbib}
\usepackage{lmodern} % Chloe: better font rendering
\usepackage[shortcuts]{extdash} 
\newcommand{\mean}[1]{$\overline{\mbox{#1}}$}
\newcommand{\median}[1]{$\hat{\mbox{#1}}$}

@@

\title{Combining network-guided GWAS to discover susceptibility mechanisms for breast cancer}
\author{Héctor Climente-González$^{1,2,3,4,\spadesuit}$, Christine Lonjou$^{1,2,3}$, Fabienne Lesueur$^{1,2,3}$, \\
GENESIS Study collaborators$^{1,2,3}$, Dominique Stoppa-Lyonnet$^{5,6,7}$, \\
Nadine Andrieu$^{1,2,3}$, Chloé-Agathe Azencott$^{3,1,2}$}
\date{\small{
  \raggedright{
  $^{1}$Institut Curie, PSL Research University, F-75005 Paris, France;\\
  $^{2}$INSERM, U900, F-75005 Paris, France;\\
  $^{3}$MINES ParisTech, PSL Research University, CBIO-Centre for Computational Biology, F-75006 Paris, France;\\
  $^{4}$RIKEN Center for Advanced Intelligence Project (AIP), Tokyo, 103-0027, Japan; \\
  $^{5}$Service de Génétique, Institut Curie, F-75005 Paris, France;\\
  $^{6}$INSERM, U830, F-75005 Paris, France;\\
  $^{7}$Université Paris Descartes.\\
  }
  \raggedright{$^{\spadesuit}$Corresponding author: \href{hector.climente@riken.jp}{hector.climente@riken.jp}\\}
}
}
\hypersetup{
  pdfauthor={Héctor Climente-González, Christine Lonjou, Fabienne Lesueur, GENESIS Study collaborators, Dominique Stoppa-Lyonnet, Nadine Andrieu, Chloé-Agathe Azencott},
  pdftitle={Combining network-guided GWAS to discover susceptibility mechanisms for breast cancer},
  pdfkeywords={},
  pdfsubject={},
  pdflang={English}}
\begin{document}

@@

\begin{description}
  \item[Conceptualization] Héctor Climente-González, Christine Lonjou, Chloé-Agathe Azencott.
  \item[Data curation] Christine Lonjou, GENESIS Study collaborators.
  \item[Formal Analysis] Héctor Climente-González, Christine Lonjou.
  \item[Funding acquisition] Dominique Stoppa-Lyonnet, Nadine Andrieu, Chloé-Agathe Azencott.
  \item[Investigation] Héctor Climente-González, Christine Lonjou.
  \item[Methodology] Héctor Climente-González, Christine Lonjou, Chloé-Agathe Azencott.
  \item[Project administration] Chloé-Agathe Azencott.
  \item[Resources] GENESIS Study collaborators, Dominique Stoppa-Lyonnet, Nadine Andrieu.
  \item[Software] Héctor Climente-González, Christine Lonjou.
  \item[Supervision] Christine Lonjou, Fabienne Lesueur, Nadine Andrieu, Chloé-Agathe Azencott.
  \item[Validation] Christine Lonjou, Fabienne Lesueur.
  \item[Visualization] Héctor Climente-González.
  \item[Writing – original draft] Héctor Climente-González.
  \item[Writing – review \& editing] Héctor Climente-González, Christine Lonjou, Fabienne Lesueur, Nadine Andrieu, Chloé-Agathe Azencott.
\end{description}
